Adaptive global optimization using graphics accelerators\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-05-26 2020/RSD_GPU/RSD2020.tex
Add Toropov as co-author

\begin{document}
\mainmatter              % start of a contribution
%
\title{Adaptive global optimization using graphics accelerators\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Adaptive global optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Konstantin Barkalov%\orcidID{0000-0001-5273-2471} 
\and Ilya Lebedev\letter%\orcidID{0000-0002-8736-0652}
}

%
\authorrunning{Konstantin Barkalov \and Ilya Lebedev} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Konstantin Barkalov and Ilya Lebedev}
%
\institute{Lobachevsky State University of Nizhni Novgorod, Russia  \\
	\email{konstantin.barkalov@itmm.unn.ru},
	\email{ilya.lebedev@itmm.unn.ru}
}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Adaptive global optimization using graphics accelerators\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Adaptive global optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{
Konstantin A. Barkalov%(ORCID 0000-0001-5273-2471)
$^1$ \and
Ilya G. Lebedev \letter%(ORCID 0000-0002-8736-0652)
$^1$ \and 
Vassili V. Toropov%(ORCID 0000-0002-7017-5055)
$^{1,2}$
}

%
\authorrunning{K.A. Barkalov \and I.G. Lebedev \and V.V. Toropov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Konstantin Barkalov and Ilya Lebedev }
%

\institute{$^1$Lobachevsky State University of Nizhny Novgorod, Nizhny Novgorod, Russia\\
\email{konstantin.barkalov@itmm.unn.ru},
\email{ilya.lebedev@itmm.unn.ru}\\
$^2$Queen Mary University of London, London, UK\\
\email{v.v.toropov@qmul.ac.uk}\\
}
